\section{Introduction}

The measurement of double Higgs production will be one of the central
physics goals of the LHC program in its recently started high-energy
phase, as well as for its future high-luminosity upgrade (HL-LHC)
which aims to accumulate a total integrated
luminosity of 3 ab$^{-1}$~\cite{ATLAS:2013hta,CMS:2013xfa}.
%
Higgs pair production~\cite{baglio} is directly sensitive to the
Higgs trilinear coupling $\lambda$ and 
provides crucial
information on the electroweak symmetry breaking mechanism.
%
It also probes the underlying strength of the Higgs interactions
at high energies, and can be used to test the composite nature of the 
Higgs boson~\cite{Giudice:2007fh,Contino:2010mh}.
%
While Standard Model (SM) cross-sections are small,
many Beyond the SM (BSM)
scenarios predict enhanced rates for double Higgs production, therefore searches have already been performed by ATLAS and CMS with Run I data~\cite{Aad:2015xja,Aad:2015uka,Aad:2014yja,Khachatryan:2015yea,Chatrchyan:2011wt}
and will continue at Run II.
%
The study of Higgs pair production will also be relevant to
any future high-energy 
collider, either at a 100 TeV circular machine~\cite{Arkani-Hamed:2015vfh,Barr:2014sga,Papaefstathiou:2015iba,Azatov:2015oxa} or at
a linear or circular electron-positron collider~\cite{Contino:2013gna}.

Analogously to single Higgs production~\cite{Dittmaier:2012vm}, 
in the SM the dominant mechanism for the production of a pair of
Higgs bosons at the LHC is 
gluon fusion (see~\cite{baglio,Frederix:2014hta} and
references therein).
%
For a center-of-mass energy of $\sqrt{s} = 14\,$TeV, the
next-to-next-to-leading order (NNLO)
total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea},
which is increased by a further few percent once
next-to-next-to-leading logarithmic
(NNLL) corrections
are accounted for~\cite{deFlorian:2015moa}.
%
Feasibility studies in the case of a SM-like Higgs boson
in the gluon-fusion channel
at the LHC have been performed for different final states, including
$b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
$b\bar{b}\tau^+\tau^-$~\cite{Baur:2003gpa,Barr:2013tda,Dolan:2012rv,Dolan:2013rja},
$b\bar{b}W^+W^-$~\cite{Dolan:2012rv,Papaefstathiou:2012qe} and
$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Wardrope:2014kya,deLima:2014dta,Barger:2013jfa}.
%
While these studies differ in their quantitative conclusions,
a consistent picture emerges 
that the ultimate precision in the determination of the Higgs trilinear
coupling $\lambda$ requires the full integrated luminosity
of the HL-LHC, $\mathcal{L}=3$ ab$^{-1}$,
and should rely on the combination of all relevant final states.


In addition to the gluon-fusion channel, Higgs pairs
can also be produced in the vector-boson fusion
channel $hhjj$~\cite{Contino:2010mh,Dolan:2013rja,Dolan:2015zja,
  Brooijmans:2014eja},
the associated production modes
$hhW$ and $hhZ$~\cite{Barger:1988jk,baglio,Cao:2015oxx}
(also known as Higgs-Strahlung),
and also in association
with top quark pairs $hht\bar{t}$~\cite{Englert:2014uqa}.
%
All these channels are challenging due to the small production
rates: at 14 TeV, the inclusive total cross-sections are
2.0 fb for VBF $hhjj$~\cite{Liu-Sheng:2014gxa},
0.5 fb for $W(Z)hh$~\cite{baglio}
and 1.0 for $hht\bar{t}$~\cite{Englert:2014uqa}.
%
The interplay between  kinematic
distributions for the
extraction of $\lambda$ from the measured
cross-sections, and the role of the associated theoretical
uncertainties, have been intensely scrutinized
recently~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
  Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha,Grigo:2013rya,Grigo:2014jma}.
%


While the SM production rates for Higgs
pairs are small, they are substantially
enhanced in a variety of BSM scenarios.
%
Feasibility studies of Higgs pair production in New Physics
models have been performed in a number of different frameworks,
including Effective Field
Theories (EFTs) with higher-dimensional
operators and anomalous 
Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa}, resonant production
in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa,Wen-Juan:2015gqg}, and Supersymmetry and
Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.
%
Since BSM dynamics modify
the kinematic distributions of the Higgs decay products, for
instance boosting the di-Higgs system,
different analysis strategies  might be required for BSM
Higgs pair searches as compared to SM measurements.


Searches for the production of Higgs pairs
have already been performed with 8 TeV Run I data
by ATLAS in the $b\bar{b}b\bar{b}$~\cite{Aad:2015uka}
and $b\bar{b}\gamma\gamma$~\cite{Aad:2014yja} final states,
and by
CMS in the same $b\bar{b}b\bar{b}$~\cite{Khachatryan:2015yea}
and $b\bar{b}\gamma\gamma$~\cite{Chatrchyan:2011wt} final
states.
%
%
In addition, ATLAS has presented~\cite{Aad:2015xja} a combination
of its di-Higgs searches in the $bb\tau\tau,$
$\gamma\gamma WW^*$, $\gamma\gamma bb$, and $bbbb$ final states.
%
Many other exotic searches involve Higgs pairs in the final
state, such as the recent
search for heavy Higgs bosons $H$~\cite{Khachatryan:2015tha}.



In the context of SM production,
the main advantage of the $b\bar{b}b\bar{b}$ final state is the
enhancement of the signal yield
from the large branching fraction of Higgs bosons into
$b\bar{b}$
pairs, ${\rm BR}\lp H\to b\bar{b}\rp\simeq 0.57$~\cite{Dittmaier:2012vm}.
%
However a measurement in this channel
needs to deal with an overwhelming QCD multi-jet background.
%
Recent studies of Higgs pair production in this
final state~\cite{Wardrope:2014kya,deLima:2014dta}
estimate that, for an integrated
luminosity of
$\mathcal{L}=3$ ab$^{-1}$,
a signal significance of around $S/\sqrt{B}\simeq 2.0$ can be obtained.
%
In these analysis, irreducible backgrounds such as $4b$ and
$t\bar{t}$ are included, however the
reducible components, in particular as $bbjj$ and
$jjjj$, are neglected.
%
These can contribute to the signal yield when 
light and charm jets are mis-identified as $b$-jets.
%
Indeed, due to both
selection effects and $b$-quark radiation in the
parton shower, the
contribution of the $2b2j$ process is as significant as
the irreducible $4b$ component.

In this work, we revisit the feasibility of SM Higgs pair production by
gluon-fusion
in the $b\bar{b}b\bar{b}$ final state at the LHC.
%
 Our strategy is based upon a a combination of traditional cut-based
 methods and multivariate analysis (MVA).
  %
  We account for  all relevant
  backgrounds, including the contribution from mis-identified
  light and charm jets.
  %
  We also assess the robustness of our analysis strategy in
  an environment with high pile-up (PU).
  %
 Our results indicate that 
  the $b\bar{b}b\bar{b}$ 
final state
alone should allow for the discovery of double Higgs production
  at the HL-LHC.
  %
  We also find that, provided the contamination from light and charm jet
  mis-identification is reduced, the observation of Higgs pairs
  in this final state may be within reach already at Run II with
  $\mathcal{L}=300$ fb$^{-1}$.
  
The structure of this paper proceeds as follows.
%
In Sect.~\ref{mcgeneration} we present the modeling of the signal
and background processes with Monte Carlo event generators.
%
In Sect.~\ref{sec:analysis}
we introduce our analysis strategy, in particular
the classification of individual events into
different categories according to their topology.
%
Results of the cut-based analysis
are then presented in Sect.~\ref{sec:results}.
%
In Sect.~\ref{sec:mva} we illustrate the enhancement of signal
significance using multivariate techniques, and
assess the robustness of our results against the effects of PU.
%
In Sect.~\ref{sec:conclusions} we conclude and outline
future studies to estimate the accuracy
in the determination of the trilinear coupling $\lambda$ and
to provide
 constraints in
BSM scenarios.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
